Human Capital Model

### 2016-02-01 Tex/paper.tex
fix typo

\begin{itemize}
\item \textbf{assumption 1} The surface temperature of bathtub and the person keeps constant.

    Since human-being is temperature-constant, and bathtub contacts the ground, we can assume that they have no heat exchange.

\item \textbf{assumption 2} The volume of water flowing away is equivalent to that of hot water at any time.

    Although water has evaporation loss and other kinds of losses,  it takes up a small proportion of the total volume. Thus we sensibly neglect them.

\item \textbf{assumption 3} The hot water from the faucet has a constant flow velocity and temperature.

\item \textbf{assumption 4} There is no convection in the water.

The temperature water in the bathtub is a relatively

@@

Figure \ref{5_p}, Figure \ref{6_p}, Figure \ref{7_p} show the temperature of water at t=240, with $u_h=40$ and $v_h=0.1, 0.2 and 0.3$
\begin{figure}[htb]
  \centering
  \includegraphics[width=8cm]{6-2.pdf}\\
  \caption{$u_h=40$, $v_h=0.1$, t=240}\label{5_p}
\end{figure}

@@

Figure 8, Figure 9, Figure 10 show the temperature at t=600
\begin{figure}[htb]
  \centering
  \includegraphics[width=8cm]{6-5.pdf}\\
  \caption{$u_h=40$,$v_h=0.1$,t=600}\label{6-5_p}
\end{figure}

\begin{figure}[htb]
  \centering
  \includegraphics[width=8cm]{10-5.pdf}\\
  \caption{$u_h=40$,$v_h=0.2$,t=240}\label{10-5_p}
\end{figure}

\begin{figure}[htb]
  \centering
  \includegraphics[width=8cm]{11-5.pdf}\\
  \caption{$u_h=40$,$v_h=0.3$,t=600}\label{11-5_p}
\end{figure}

It indicates that keep $u_h$, temperature increases when $v_h$ increases, and the system becomes more stable as time goes on. It proves that our model is sensible.

Figure 11, Figure 12, Figure 13 show the temperature of water at t=240, with $v_h=0.2$ and $u_h=30, 40 and 50$

\begin{figure}[htb]
  \centering
  \includegraphics[width=8cm]{8-2.pdf}\\
  \caption{$u_h=30$,$v_h=0.2$,t=240}\label{8-2_p}
\end{figure}

\begin{figure}[htb]
  \centering
  \includegraphics[width=8cm]{10-2.pdf}\\
  \caption{$u_h=40$,$v_h=0.2$,t=240}\label{10-2_p}
\end{figure}

\begin{figure}[htb]
  \centering
  \includegraphics[width=8cm]{4-2.pdf}\\
  \caption{$u_h=50$,$v_h=0.2$,t=240}\label{4-2_p}
\end{figure}

Figure 14, Figure 15, Figure 16 show the temperature at t=600

\begin{figure}[htb]
  \centering
  \includegraphics[width=8cm]{8-5.pdf}\\
  \caption{$u_h=30$,$v_h=0.2$,t=600}\label{8-5_p}
\end{figure}

\begin{figure}[htb]
  \centering
  \includegraphics[width=8cm]{10-5.pdf}\\
  \caption{$u_h=40$,$v_h=0.2$,t=600}\label{10-5_p}
\end{figure}

\begin{figure}[htb]
  \centering
  \includegraphics[width=8cm]{4-5.pdf}\\
  \caption{$u_h=50$,$v_h=0.2$,t=600}\label{4-5_p}
\end{figure}

It indicates that keep $v_h$, temperature increases when $u_h$ increases, and the system becomes more stable as time goes on. It proves that our model is sensible.

Comparing the temperature distribution of each strategy, with least water waste, we choose $v_h=0.2$, $u_h=40$ as the best strategy to keep the temperature.

@@

\subsection{Parameters of Bathtub}
\label{sec:parameters of bathtub}
\begin{itemize}
\item We change the shape of the bathtub to sphere and cylinder to get the best strategy. The result shows that the bathtub with the shape of sphere is the most effective in keeping temperature.
\begin{center}
\begin{tabular}{c|c|c}
\hline
 Shape     &$v_h$  &$u_h$        \\ \hline
 Square    &0.2             & 40              \\ \hline
 Sphere    &0.15            & 40              \\ \hline
 Cylinder  &0.2             & 45              \\ \hline
\end{tabular}
\end{center}
     \item We change the volume of the bathtub without changing the proportion. The result in the following table shows that with the same $v_h$, $u_h$ increases as volume increases; with the same $u_h$, $v_h$ increases as volume increases.
\end{itemize}

\subsection{Parameters of Person}
\label{sec:parameters of person}
\begin{itemize}
\item Comparing the temperature graph with different shape of the person, we found when the shape gets more regular, $u_h$, $v_h$ decreases relatively.
\item Change the volume of the person. The result shows that, $u_h$, $v_h$ for best strategy increases when the volume increases.
\item Change the surface temperature of the person to get the best strategy. The result shows no noticeable change.
    \begin{center}
\begin{tabular}{c|c|c}
\hline
 Surface Temperature     &$v_h$  &$u_h$        \\ \hline
 $u_2=33.5$    &0.2             & 40              \\ \hline
 $u_2=33.5$    &0.15            & 40              \\ \hline
 $u_2=33.5$  &0.2             & 45              \\ \hline
\end{tabular}
\end{center}
\end{itemize}

\subsection{Effects of Motion}
\label{sec:effects of motion}
When the person in the bathtub makes motions, the heat exchange coefficient between the person and water ${\gamma}_2$ increases. That means heat exchange between water and the person increases. In another aspect, the air above flows, so that evaporation heat of water increases. Water loses more heat.

@@

The effect is that more heat is needed to keep the temperature, consequently $u_h$ as the best strategy increases to keep the temperature.

@@

\begin{itemize}
\item Our model make good use of thermology knowledge so it can reflect the situation in the real world realistically.
\item Our model build a 3D geometry to simulate the research object so it can show the exact situation.
\item Our model operates with different strategies and display the result by 3D geometry graph, so they could be compared in a visible way.
\item Our model proves the effect of time.
\end{itemize}

@@

\begin{itemize}
\item We assume that the water is still. In fact, streams flow and fluid dynamic is better taken into consideration. The actual situation is much complicated.
\item The model of the person should be more realistic. In fact, model of human body includes hands, legs or other parts, and the surface of human skin isn't even.
\item The condensation of water should be taken into consideration. Water that evaporate become water vapour, and some will condense into water on the bathtub.
\end{itemize}

@@

\begin{itemize}
\item Obviously, the water exchange thermal energy directly with the air. That's why you can see water vapour float above the water. The temperature of water decreases as a result of the heat exchange.
\item On the other hand, the bathtub is cooler than the water on most occasions. It's reasonable that the bathtub absorbs heat from the water. However, the bathtub conduct heat easily, while in this way the air's temperature rises. In other words, the temperature of water decreases faster.
\end{itemize}
From statement above, you may understand our bathtub can't stay in an even temperature evenly. Consequently we have some suggestions for you, if you'd like to enjoy more during your bath :
\begin{itemize}
\item To keep the water warm and relax yourself, you may turn the faucet on. Water-in in high temperature loses it's energy quickly, and water-in in low temperature is unable to warm your surrounding. It's best that you set the speed of the water-in at 0.2kg/s, and temperature at $40\,^{\circ}\mathrm{C}$.
\item Further more, your movement effects the water. It would be great if you stay still, but it doesn't count too much. For a better temperature-keeping situation, you may add some bubble bath additive to decrease the temperature loss.
\end{itemize}
We hope you enjoy your bath.

>>>>

\begin{itemize}
\item \textbf{assumption 1} If an employee has probability to
  promote, he won't churn.

The possibility of the unforeseen accidents, which could force an
employee to leave his position,is neglected.Human nature, an employee
will stay at his position to chase for higher level.

\item \textbf{assumption 2} For a vacancy,if there exists an
  employee measures up to it already,ICM won't recruit for it.

Since recruiting good people is difficult, time consuming and
expensive according to issue 5,it is wasteful to recruit for a
position if an employee can promote to it.

\item \textbf{assumption 3} Demotion won't occur.

\item \textbf{assumption 4} Administrative clerk won't promote or be
  transferred.

@@

\begin{figure}[htb]
  \centering
  \includegraphics[width=8cm]{6-2.pdf}\\
  \caption{$u_h=40$, $v_h=0.1$, t=240}\label{5_p}
\end{figure}

@@

Figure \ref{5_p}, Figure \ref{6_p}, Figure \ref{7_p} show the temperature of water at t=240, with $u_h=40$ and $v_h=0.1, 0.2 and 0.3$

\begin{figure}[htb]
  \centering
  \includegraphics[width=8cm]{6-5.pdf}\\
  \caption{$u_h=40$,$v_h=0.1$,t=600}\label{8_p}
\end{figure}

\begin{figure}[htb]
  \centering
  \includegraphics[width=8cm]{10-5.pdf}\\
  \caption{$u_h=40$,$v_h=0.2$,t=240}\label{9_p}
\end{figure}

\begin{figure}[htb]
  \centering
  \includegraphics[width=8cm]{11-5.pdf}\\
  \caption{$u_h=40$,$v_h=0.3$,t=600}\label{10_p}
\end{figure}

Figure \ref{8_p}, Figure \ref{9_p}, Figure \ref{10_p} show the temperature at t=600

It indicates that when $u_h$ is constant, temperature increases when $v_h$ increases, and the system becomes more stable as time goes on. It proves that our model is sensible.

\begin{figure}[htb]
  \centering
  \includegraphics[width=8cm]{8-2.pdf}\\
  \caption{$u_h=30$,$v_h=0.2$,t=240}\label{11_p}
\end{figure}

\begin{figure}[htb]
  \centering
  \includegraphics[width=8cm]{4-2.pdf}\\
  \caption{$u_h=50$,$v_h=0.2$,t=240}\label{12_p}
\end{figure}

Figure \ref{11_p}, Figure \ref{6_p}, Figure \ref{12_p} show the temperature of water at t=240, with $v_h=0.2$ and $u_h=30, 40 and 50$

\begin{figure}[htb]
  \centering
  \includegraphics[width=8cm]{8-5.pdf}\\
  \caption{$u_h=30$,$v_h=0.2$,t=600}\label{13_p}
\end{figure}

\begin{figure}[htb]
  \centering
  \includegraphics[width=8cm]{4-5.pdf}\\
  \caption{$u_h=50$,$v_h=0.2$,t=600}\label{14_p}
\end{figure}

Figure \ref{13_p}, Figure \ref{9_p}, Figure \ref{14_p} show the temperature at t=600

It indicates that when $v_h$ is constant, temperature increases when $u_h$ increases, and the system becomes more stable as time goes on. It proves that our model is sensible.

Comparing the temperature distributions of each strategy, with least water waste, we choose $v_h=0.2$, $u_h=40$ as the best strategy to keep the temperature.

@@

\subsection{Parameters of Bathtub}
\label{sec:parameters of bathtub}

\begin{table}
\begin{center}
\begin{tabular}{c|c|c}
\hline
 Shape     &$v_h$  &$u_h$        \\ \hline
 Square    &0.2             & 40              \\ \hline
 Sphere    &0.15            & 40              \\ \hline
 Cylinder  &0.2             & 45              \\ \hline
\end{tabular}
\end{center}
\caption{Shape of Bathtub}\label{4_t}
\end{table}

\begin{itemize}

\item We change the shape of the bathtub to sphere and cylinder to get the best strategy. The result shown in Table \ref{4_t} that the bathtub with the shape of sphere is the most effective in keeping temperature.

     \item We change the volume of the bathtub without changing the proportion. The result in the following table shows that with the same $v_h$, $u_h$ increases as volume increases; with the same $u_h$, $v_h$ increases as volume increases.
\end{itemize}

\subsection{Parameters of Person}
\label{sec:parameters of person}
\begin{itemize}
\item Comparing the temperature graphs with different shapes of the bather, we find when the shape gets more regular, $u_h$, $v_h$ decreases relatively.
\item Change the volume of the bather. The result shows that, $u_h$, $v_h$ for best strategy increases when the volume increases.
\item Change the surface temperature of the bather to get the best strategy. The result shows no noticeable change.
\begin{table}
\begin{center}
\begin{tabular}{c|c|c}
\hline
 Surface Temperature     &$v_h$  &$u_h$        \\ \hline
 $u_2=33.5$    &0.2             & 40              \\ \hline
 $u_2=33.5$    &0.15            & 40              \\ \hline
 $u_2=33.5$  &0.2             & 45              \\ \hline
\end{tabular}
\end{center}
\caption{Surface Temperature}\label{5_t}
\end{table}
\end{itemize}

\subsection{Effects of Motion}
\label{sec:effects of motion}
When the bather in the bathtub makes motions, the heat exchange coefficient between the bather and water ${\gamma}_2$ increases. That means heat exchange between water and the bather increases. In another aspect, the air above flows, so that evaporation heat of water increases. Water loses more heat.

@@

@@

\begin{itemize}
\item Our model makes good use of thermology knowledge so it can reflect the situation in the real world realistically.
\item Our model builds a 3D geometry to simulate the research object so it can show the exact situation.
\item Our model operates with different strategies and displays the result by 3D geometry graph, so they could be compared in a visible way.
\item Our model proves the effect of time.
\end{itemize}

@@

\begin{itemize}
\item We assume that the water is still. In fact, it is better to take the streams flow and fluid dynamic into consideration. The actual situation is much more complicated.
\item The model of the bather should be more realistic. In fact, model of human body includes hands, legs or other parts, and the surface of human skin isn't even.
\item The condensation of water should be taken into consideration. Water that evaporates become water vapour, and some will condense into water on the bathtub.
\end{itemize}

@@

\begin{itemize}
\item Obviously, the water exchanges thermal energy directly with the air. That's why you can see water vapour floats above the water. The temperature of water decreases as a result of the heat exchange.
\item On the other hand, the bathtub is cooler than the water in most occasions. It's reasonable that the bathtub absorbs heat from the water. However, the bathtub conducts heat easily. In this way the air's temperature rises. In other words, the temperature of water decreases faster.
\end{itemize}
From statement above, you may understand our bathtub can't stay in an constant temperature evenly. Consequently we have some suggestions for you, if you'd like to enjoy more during your bath :
\begin{itemize}
\item To keep the water warm and relax yourself, you may turn the faucet on. Water-in in high temperature loses it's energy quickly, and water-in in low temperature is unable to warm your surrounding. We recommend you set the speed of the water-in at 0.2kg/s, and temperature at $40\,^{\circ}\mathrm{C}$.
\item Further more, your movement effects the water. It would be great if you stay still, but it doesn't count too much. For a better temperature-keeping situation, you may add some bubble bath additive to decrease the temperature loss.
\end{itemize}
We hope you enjoy your bath.
